---
title: "677 Assignment 1"
author: "Haoyu Li"
date: "2021/2/11"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

First, we calculate the alpha value, which is the probability of type 1 error. In the case that the textbbok mentioned, p=0.6 when m=60 people have been cured, and the total number of people are n=100. The probability function is writen as $$\alpha(p)=\sum_{m\le{k}\le{n}}b(n,p,k)=\sum_{60\le{k}\le{100}}b(100,0.6,k)$$
```{r}
# alpha when p=0.6
m1=rep(0,times=40)
P1=rep(0,times=40)
for(i in 0:40){
  m1[i]=i+60
  P1[i]=pbinom(q=100,size=100,prob=0.6)-pbinom(q=m1[i]-1,size=100,prob=0.6)
}
a=data.frame(cbind(m1,P1))
```

Next, we calculate the probability of type 2 error, which is beta value. The probability function can be writen as the function of alpha, since beta value = 1 - alpha value. In this case, p=0.8 when m=80 people have been cured
```{r}
m2=rep(0,times=20)
P2=rep(0,times=20)
for(i in 0:20){
  m2[i]=80-i
  P2[i]=pbinom(q=m2[i]-1,size=100,prob=0.8)
}
b=data.frame(cbind(m2,P2))
```

Now, we apply the criteria that alpha and beta value are less than 0.05 to filter out the value for m
```{r}
m_a=a[which(a$P1<0.05),1]
min(m_a)
m_b=b[which(b$P2<0.05),1]
max(m_b)
intersect(m_a,m_b)
```

Thus, we get the minimum m value for 69, which can make the alpha value less likely and m value for 73 which can make the beta value less likely.

## power curve
write a program PowerCurve to plot, for n = 100 and selected values of m,
the function alpha(p), for p ranging from .4 to 1.

For the x-axis, this is the probability that new drug is effective.
```{r}
p=seq(from=0.4,to=1,length=100)
```

For the y-axis, that is the probability of the type 1 error
```{r}
#when m=69
alpha1=rep(0,times=length((p)))
for(i in 1:100){
  alpha1[i]=pbinom(q=100,size=100,prob=p[i])-pbinom(q=68,size=100,prob=p[i])
}
```

```{r}
#for m=73
alpha2=rep(0,times=length((p)))
for(i in 1:100){
  alpha2[i]=pbinom(q=100,size=100,prob=p[i])-pbinom(q=72,size=100,prob=p[i])
}
``` 

We combine alpha1 and alpha2
```{r}
type_error=data.frame(cbind(p,alpha1,alpha2))
```

Now we can plot our curve
```{r}
powercurve=ggplot(data=type_error,mapping=aes(x=p))+
  geom_line(mapping=aes(y=alpha1))+
  geom_line(mapping=aes(y=alpha2))+
  labs(x="p",y="a(p)",title="The power curve")+
  theme(title=element_text(hjust=0.5,size=10))
powercurve
```

Finally, we add the box which range from 0.05 to 0.95
```{r}
powercurve+
  geom_segment(mapping=aes(x=0.6,xend=0.8,y=0.05,yend=0.05))+
  geom_segment(mapping=aes(x=0.6,xend=0.8,y=0.95,yend=0.95))+
  geom_segment(mapping=aes(x=0.6,xend=0.6,y=0.05,yend=0.95))+
  geom_segment(mapping=aes(x=0.8,xend=0.8,y=0.05,yend=0.95))
```

Note: I collaborate with yuxin zeng to finish this assignment.




